Recursive algorithms, branching coefficients and applications

### 2010-07-06 AffineLieAlgebras/InformalNotes/article.tex
Merged V.D. changes - section on conformal embeddings of semisimple subalgebras is left out.

Usually only the maximal reductive subalgebras are considered since the case of non-maximal subalgebra can be obtained using the chain of maximal injections. In this paper we find the recurrent properties for branching coefficients that generalise the relations obtained earlier (see the paper \cite{ilyin812pbc} and the references therein) to the case of non-maximal reductive subalgebra. The result is formulated in terms of new injection fan called "the subtracted fan". Using this new tools we formulate simple and explicit algorithm for computations of branching coefficients which is applicable to the non-maximal subalgebras of finite-dimensional and affine Lie algebras.

@@

The paper is organised as follows. In the subsection \ref{sec:notation}  we fix the notations. In the Section \ref{sec:recurr-form-branch} we derive the subtracted recurrent formula for anomalous branching coefficients and describe the decomposition algorithm for integrable highest weight modules $L_{\mathfrak{g}}$ with respect to a reductive subalgebra $\mathfrak{a}\subset \mathfrak{g}$ (subsection \ref{sec:algorithm}). In the Section \ref{sec:finite-dimens-lie} we present several simple examples for finite-dimensional Lie algebras. The affine Lie algebras and their applications in CFT models are considered in Section \ref{sec:phys-appl}. We conclude the paper with a review of obtained results. Possible further developments are discussed (Section \ref{sec:conclusion}).

@@

We use the following notations adopted from the paper \cite{ilyin812pbc}.

@@

It is important whether there exist the positive roots $\alpha\in \Delta$ such that $\pi_{\mathfrak{a}}\alpha=0$. These roots are orthogonal to $P_{\mathfrak{a}}$. Let's denote the subset of such roots by $\Delta^{+}_{\bot}
=\left\{\alpha\in\Delta_{\mathfrak{g}}^{+}:
\forall \beta\in \Delta_{\mathfrak{a}}^{+},\; \alpha\bot\beta \right\}$.

Notice that if $\Delta^{+}_{\bot}\neq \emptyset$ the Weyl reflections
corresponding to the positive roots of $\Delta^{+}_{\bot}$ generate a subgroup
$W_{\bot}$ of the Weyl group $W$. Consider any two positive roots $\alpha,\;
\beta\in \Delta^{+}_{\bot}$ and the corresponding Weyl reflections
$\omega_{\alpha},\; \omega_{\beta}\in W_{\bot}$.  Since roots $\beta\in \Delta_{\mathfrak{a}}$ are invariant with respect to $\omega_{\alpha}, \; \omega_{\beta}$ they
are also invariant under the action of $\omega_{\gamma}=\omega_{\alpha}\cdot \omega_{\beta}$.
So the subgroup $W_{\bot}$ preserves $\Delta_{\mathfrak{a}}$.

Thus we have obtained the system $\Delta_{\bot}$ orthogonal $P_{\mathfrak{a}}$ and invariant with respect to  $W_{\bot}$. It
can be considered as the root system of a subalgebra $\mathfrak{a}_{\bot}\subset \mathfrak{g}$.

@@

\subsection{Algorithm for the recursive computation of the branching coefficients}
\label{sec:algorithm}

@@

\subsubsection{Embeddings of semisimple subalgebras}
\label{sec:embedd-semis-subalg}

Consider the embedding $\mathfrak{a}\subset \mathfrak{g}$ where
$\mathfrak{a}=\hat A_1\oplus \hat A_1$ and $\mathfrak{g}= \hat A_3$,
which is the affine extension of the special embedding $A_1\oplus A_1\subset A_3$.
To construct this injection we use the method presented in \cite{vasilevich1986method}.
We start with the 4-dimensional module $L_{A_1\oplus A_1}^{(1,1)}$. Its diagram
$$\mathcal{N}_{A_1\oplus A_1}^{(1,1)}= \left\{\nu_1=(1,1),\; \nu_2=(-1,1),\; \nu_3=(1,-1),\; \nu_4=(-1,-1)\right\}$$
is presented in Figure \ref{fig:A_1+A_1_to_A3}.

\begin{figure}[h!tb]
  \begin{multicols}{2}
    \hfill
    \includegraphics[width=50mm]{A_1+A_1_to_A3.eps}
    \hfill
    \caption{The special embedding  $A_1\oplus A_1\subset A_3$ is based on this module}
    \label{fig:A_1+A_1_to_A3}
    \hfill
    \includegraphics[width=50mm]{A1+A1-A3.eps}
    \hfill
    \caption{Embedded roots for the special embedding  $A_1\oplus A_1\subset A_3$}
    \label{fig:A1+A1-A3}
  \end{multicols}
\end{figure}

For the matrix elements of representation of Cartan subalgebra generators $b_1,b_2$ in
the Weyl basis we have $d(b_i)=\mathrm{diag}\left(\frac{2(\nu_1,\alpha_i)}
{(\alpha_i,\alpha_i)},\frac{2(\nu_2,\alpha_i)}{(\alpha_i,\alpha_i)},
\frac{2(\nu_3,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_4,\alpha_i)}
{(\alpha_i,\alpha_i)}\right)$ \cite{vasilevich1986method},
thus $d(b_1)=\mathrm{diag}(1,-1,1,-1),\; d(b_2)=\mathrm{diag}(1,1,-1,-1)$.
The embedded roots $\alpha_1,\alpha_2$ of $A_1\oplus A_1$ in terms of roots $\tilde{\alpha}_i$ of $A_3$ are
\begin{equation}
  \label{eq:37}
  \begin{array}{l}
     \alpha_1=\frac{1}{2}(\tilde{\alpha}_1+\tilde{\alpha}_3)\\
     \alpha_2=\frac{1}{2}(\tilde{\alpha}_1+2\tilde{\alpha}_2+\tilde{\alpha}_3)
  \end{array}
\end{equation}
(See Figure \ref{fig:A1+A1-A3}.)

This injection is characterised by the embedding indices $(2,2)$ and is conformal,
since $c(A_1\oplus A_1)=c(A_1)+c(A_1)=2\frac{x_e \mathrm{dim}(A_1)}{x_e+2}=\frac{\mathrm{dim}A_3}{5}=c(A_3)$.

We are interested in the reduction of the fundamental modules of $\hat A_3$.
Four fundamental weights of level 1 have the following coordinates in the orthogonal basis: 
\begin{equation}
  \begin{array}{lll}
     w_0 & = & (0,0,0,0;1;0),\\
     w_1 & = & (\frac{3}{4},-\frac{1}{4},-\frac{1}{4},-\frac{1}{4}; 1; 0),\\
     w_2 & = & (\frac{1}{2},\frac{1}{2},-\frac{1}{2},-\frac{1}{2}; 1; 0),\\
     w_3 & = & (\frac{1}{4},\frac{1}{4},\frac{1}{4},-\frac{3}{4}; 1; 0). \\
  \end{array}
\end{equation}

For the sets of positive roots $\Delta^{+}$ and $\Delta_{\mathfrak{a}}^{+}$ we have
\begin{equation}
  \label{eq:38}
  \begin{array}{lll}
    \Delta^{+} &=&\left\{\co{\Delta}^{+}=\{\tilde{\alpha}_1, \tilde{\alpha}_2, \tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2, \tilde{\alpha}_2+\tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2+\tilde{\alpha}_3\};\right.\\
    &\; & \quad\left.\co{\Delta}+n\delta;\;     +n\delta\;\mbox{with multiplicity}\; 3;\; n=1,2,\dots,\right\}\\
    \Delta_{\mathfrak{a}}^{+} &=& \{  \alpha_1,\alpha_2;\;\pm \alpha_1+n\delta,\pm \alpha_2+n\delta;\; +n\delta\; \mbox{with multiplicity} \; 2;\; n=1,2,\dots\}\\
  \end{array}
\end{equation}
The set $\Delta^{+}_{\bot}$ is empty.
The fan $\Gamma _{\frak{a}\subset \frak{g}}$ is shown in the Figure \ref{fig:A1+A1-A3_fan}.
The coordinates of fan element finite part are given in the basis of $A_1\oplus A_1$ fundamental roots.
The fan elements $\gamma$ are marked by crosses if  $s(\gamma)=1$ and by diamonds if $s(\gamma)=-1$.
\begin{figure}[h!tb]
  \includegraphics[width=135mm]{A1+A1-A3_fan.eps}
  \caption{The fan for the special embedding $\hat A_1\oplus\hat A_1\subset\hat A_3$}
  \label{fig:A1+A1-A3_fan}
\end{figure}

We limit our calculations by the first 5 grades.
\begin{figure}[t]
%\begin{figure}[p]
%  \hspace*{-1cm}
  \includegraphics[width=135mm]{A1+A1-A3_anom.eps}
  \caption{Projected anomalous weights for $L^{w_2}_{\hat A_3\downarrow \hat{A_1}\oplus\hat{A_1}}$}
  \label{fig:A1+A1-A3_anom}
\end{figure}

The set of anomalous weights $\widehat{\Psi_{\hat A_3}^{(\mu)}}$
and its projection $\pi_{\mathfrak{a}}\left(\widehat{\Psi^{(\mu)}}\right)$ for
$\mu=w_2=(0,1,0;1;0)$ is shown in the Figure \ref{fig:A1+A1-A3_anom}.
Coordinates of the finite part are given in the basis of fundamental weights of $A_1\oplus A_1$.
The weights are marked by crosses if $\epsilon(\omega)=1$ and by diamonds otherwise.

The anomalous branching coefficients for the module $L^{(w_2)}$ are shown in the Figure  \ref{fig:A1+A1-A3_branching}.
Inside the chamber $\bar{C_{\mathfrak{a}}}$ the anomalous branching coefficients coinside with
the branching coefficients of $L^{w_2}_{\hat A_3\downarrow \hat{A_1}\oplus\hat{A_1}}$
and are marked by the stars in the Figure \ref{fig:A1+A1-A3_branching}.
\begin{figure}[b]
%\begin{figure}[p]
%  \hspace*{-1cm}
  \includegraphics[width=135mm,height=85mm]{A1+A1-A3_branching.eps}
  \caption{Anomalous branching coefficients for $L^{w_2}_{\hat A_3\downarrow \hat{A_1}\oplus\hat{A_1}}$}
  \label{fig:A1+A1-A3_branching}
\end{figure}

Treating analogously the modules $L^{w_0}_{\hat A_3}, L^{w_1}_{\hat A_3}, L^{w_3}_{\hat A_3}$
we get the following set of branching rules
 \begin{equation}
   \label{eq:39}
   \begin{array}{ll}
     L^{(0,0,0;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(0;2;0)}\otimes L_{\hat{A_1}}^{(0;2;0)} \\
     L^{(1,0,0;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(1;2;0)}\otimes L_{\hat{A_1}}^{(1;2;0)} \\
     L^{(0,1,0;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & \left( L_{\hat{A_1}}^{(2;2;0)}\otimes L_{\hat{A_1}}^{(0;2;0)}\right) \oplus \left( L_{\hat{A_1}}^{(0;2;0)}\otimes L_{\hat{A_1}}^{(2;2;0)}\right) \\
     L^{(0,0,1;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(1;2;0)}\otimes L_{\hat{A_1}}^{(1;2;0)} \\     
   \end{array}
 \end{equation}

Now we can construct the modular invariant partition function for WZW-model with the chiral algebra $\hat{A}_1\oplus \hat{A}_1$.
\begin{eqnarray*}
  \label{eq:40}
  Z=\left|\chi_{(0;2;0)}\chi_{(0;2;0)}\right|^2+2\left|\chi_{(1;2;0)}\chi_{(1;2;0)}\right|^2+ \left|\chi_{(2;2;0)}\chi_{(0;2;0)}+\chi_{(0;2;0)}\chi_{(2;2;0)}\right|^2=\\
  \left|\chi_{(0;2;0)}\right|^4+2\left|\chi_{(1;2;0)}\right|^4+ 4\left|\chi_{(2;2;0)}\chi_{(0;2;0)}\right|^2
\end{eqnarray*}

By this example we have illustrated the mechanism of our algorithm.
We want to remind that the proposed method is universal and can be applied to
an arbitrary pair of affine Lie algebras $\mathfrak{a}\subset\mathfrak{g}$.

\subsection{Coset models}
\label{sec:coset-models}

>>>>

Usually only the maximal reductive subalgebras are considered since the case of non-maximal subalgebra
can be obtained using the chain of maximal injections. In this paper we find the recurrent properties
for branching coefficients that generalise the relations obtained earlier (see the paper \cite{ilyin812pbc}
and the references therein) to the case of non-maximal reductive subalgebra. The result is formulated in
terms of the new injection fan called "the subtracted fan". Using this new tools we formulate a simple and
explicit algorithm for computations of branching coefficients which is applicable to the non-maximal
subalgebras of finite-dimensional and affine Lie algebras.

@@

The paper is organised as follows. In the subsection \ref{sec:notation}  we fix the notations.
In the Section \ref{sec:recurr-form-branch} we derive the subtracted recurrent formula for anomalous
branching coefficients and describe the decomposition algorithm for integrable highest weight modules
$L_{\mathfrak{g}}$ with respect to a reductive subalgebra $\mathfrak{a}\subset \mathfrak{g}$
(subsection \ref{sec:algorithm}). In the Section \ref{sec:finite-dimens-lie} we present several
simple examples for finite-dimensional Lie algebras. The affine Lie algebras and their applications in
CFT models are considered in Section \ref{sec:phys-appl}.
Possible further developments are discussed (Section \ref{sec:conclusion}).

@@

We use the following notations:

@@

Consider the positive roots $\alpha\in \Delta$ orthogonal to $P_{\mathfrak{a}}$. Denote the subset of such roots by $\Delta^{+}_{\bot}
=\left\{\alpha\in\Delta_{\mathfrak{g}}^{+}:
\forall \beta\in \Delta_{\mathfrak{a}}^{+},\; \alpha\bot\beta \right\}$.
Notice that if $\Delta^{+}_{\bot}\neq \emptyset$ the corresponding Weyl reflections
generate a subgroup $W_{\bot}$ of the group $W$. Consider the roots $\alpha,\;
\beta\in \Delta^{+}_{\bot}$ and the corresponding reflections
$\omega_{\alpha},\; \omega_{\beta}\in W_{\bot}$.  Since the roots in $\Delta_{\mathfrak{a}}$
are invariant with respect to $\omega_{\alpha}, \; \omega_{\beta}$ they
are also invariant under the product $\omega_{\gamma}=\omega_{\alpha}\cdot \omega_{\beta}$
and the subgroup $W_{\bot}$ preserves the roots in $\Delta_{\mathfrak{a}}$.
The system $\Delta_{\bot}$
can be considered as the root system of a subalgebra $\mathfrak{a}_{\bot}\subset \mathfrak{g}$.

@@

\subsection{Algorithm for recursive computation of branching coefficients}
\label{sec:algorithm}

@@

% \subsubsection{Embeddings of semisimple subalgebras}
% \label{sec:embedd-semis-subalg}
% 
% Consider the embedding $\mathfrak{a}\subset \mathfrak{g}$ where
% $\mathfrak{a}=\hat A_1\oplus \hat A_1$ and $\mathfrak{g}= \hat A_3$,
% which is the affine extension of the special embedding $A_1\oplus A_1\subset A_3$.
% To construct this injection we use the method presented in \cite{vasilevich1986method}.
% We start with the 4-dimensional module $L_{A_1\oplus A_1}^{(1,1)}$. Its diagram
% $$\mathcal{N}_{A_1\oplus A_1}^{(1,1)}= \left\{\nu_1=(1,1),\; \nu_2=(-1,1),\; \nu_3=(1,-1),\; \nu_4=(-1,-1)\right\}$$
% is presented in Figure \ref{fig:A_1+A_1_to_A3}.
% 
% \begin{figure}[h!tb]
%   \begin{multicols}{2}
%     \hfill
%     \includegraphics[width=50mm]{A_1+A_1_to_A3.eps}
%     \hfill
%     \caption{The special embedding  $A_1\oplus A_1\subset A_3$ is based on this module}
%     \label{fig:A_1+A_1_to_A3}
%     \hfill
%     \includegraphics[width=50mm]{A1+A1-A3.eps}
%     \hfill
%     \caption{Embedded roots for the special embedding  $A_1\oplus A_1\subset A_3$}
%     \label{fig:A1+A1-A3}
%   \end{multicols}
% \end{figure}
% 
% For the matrix elements of representation of Cartan subalgebra generators $b_1,b_2$ in
% the Weyl basis we have $d(b_i)=\mathrm{diag}\left(\frac{2(\nu_1,\alpha_i)}
% {(\alpha_i,\alpha_i)},\frac{2(\nu_2,\alpha_i)}{(\alpha_i,\alpha_i)},
% \frac{2(\nu_3,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_4,\alpha_i)}
% {(\alpha_i,\alpha_i)}\right)$ \cite{vasilevich1986method},
% thus $d(b_1)=\mathrm{diag}(1,-1,1,-1),\; d(b_2)=\mathrm{diag}(1,1,-1,-1)$.
% The embedded roots $\alpha_1,\alpha_2$ of $A_1\oplus A_1$ in terms of roots $\tilde{\alpha}_i$ of $A_3$ are
% \begin{equation}
%   \label{eq:37}
%   \begin{array}{l}
%      \alpha_1=\frac{1}{2}(\tilde{\alpha}_1+\tilde{\alpha}_3)\\
%      \alpha_2=\frac{1}{2}(\tilde{\alpha}_1+2\tilde{\alpha}_2+\tilde{\alpha}_3)
%   \end{array}
% \end{equation}
% (See Figure \ref{fig:A1+A1-A3}.)
% 
% This injection is characterised by the embedding indices $(2,2)$ and is conformal,
% since $c(A_1\oplus A_1)=c(A_1)+c(A_1)=2\frac{x_e \mathrm{dim}(A_1)}{x_e+2}=\frac{\mathrm{dim}A_3}{5}=c(A_3)$.
% 
% We are interested in the reduction of the fundamental modules of $\hat A_3$.
% Four fundamental weights of level 1 have the following coordinates in the orthogonal basis: 
% \begin{equation}
%   \begin{array}{lll}
%      w_0 & = & (0,0,0,0;1;0),\\
%      w_1 & = & (\frac{3}{4},-\frac{1}{4},-\frac{1}{4},-\frac{1}{4}; 1; 0),\\
%      w_2 & = & (\frac{1}{2},\frac{1}{2},-\frac{1}{2},-\frac{1}{2}; 1; 0),\\
%      w_3 & = & (\frac{1}{4},\frac{1}{4},\frac{1}{4},-\frac{3}{4}; 1; 0). \\
%   \end{array}
% \end{equation}
% 
% For the sets of positive roots $\Delta^{+}$ and $\Delta_{\mathfrak{a}}^{+}$ we have
% \begin{equation}
%   \label{eq:38}
%   \begin{array}{lll}
%     \Delta^{+} &=&\left\{\co{\Delta}^{+}=\{\tilde{\alpha}_1, \tilde{\alpha}_2, \tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2, \tilde{\alpha}_2+\tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2+\tilde{\alpha}_3\};\right.\\
%     &\; & \quad\left.\co{\Delta}+n\delta;\;     +n\delta\;\mbox{with multiplicity}\; 3;\; n=1,2,\dots,\right\}\\
%     \Delta_{\mathfrak{a}}^{+} &=& \{  \alpha_1,\alpha_2;\;\pm \alpha_1+n\delta,\pm \alpha_2+n\delta;\; +n\delta\; \mbox{with multiplicity} \; 2;\; n=1,2,\dots\}\\
%   \end{array}
% \end{equation}
% The set $\Delta^{+}_{\bot}$ is empty.
% The fan $\Gamma _{\frak{a}\subset \frak{g}}$ is shown in the Figure \ref{fig:A1+A1-A3_fan}.
% The coordinates of fan element finite part are given in the basis of $A_1\oplus A_1$ fundamental roots.
% The fan elements $\gamma$ are marked by crosses if  $s(\gamma)=1$ and by diamonds if $s(\gamma)=-1$.
% \begin{figure}[h!tb]
%   \includegraphics[width=135mm]{A1+A1-A3_fan.eps}
%   \caption{The fan for the special embedding $\hat A_1\oplus\hat A_1\subset\hat A_3$}
%   \label{fig:A1+A1-A3_fan}
% \end{figure}
% 
% We limit our calculations by the first 5 grades.
% \begin{figure}[t]
% %\begin{figure}[p]
% %  \hspace*{-1cm}
%   \includegraphics[width=135mm]{A1+A1-A3_anom.eps}
%   \caption{Projected anomalous weights for $L^{w_2}_{\hat A_3\downarrow \hat{A_1}\oplus\hat{A_1}}$}
%   \label{fig:A1+A1-A3_anom}
% \end{figure}
% 
% The set of anomalous weights $\widehat{\Psi_{\hat A_3}^{(\mu)}}$
% and its projection $\pi_{\mathfrak{a}}\left(\widehat{\Psi^{(\mu)}}\right)$ for
% $\mu=w_2=(0,1,0;1;0)$ is shown in the Figure \ref{fig:A1+A1-A3_anom}.
% Coordinates of the finite part are given in the basis of fundamental weights of $A_1\oplus A_1$.
% The weights are marked by crosses if $\epsilon(\omega)=1$ and by diamonds otherwise.
% 
% 
% The anomalous branching coefficients for the module $L^{(w_2)}$ are shown in the Figure  \ref{fig:A1+A1-A3_branching}.
% Inside the chamber $\bar{C_{\mathfrak{a}}}$ the anomalous branching coefficients coinside with
% the branching coefficients of $L^{w_2}_{\hat A_3\downarrow \hat{A_1}\oplus\hat{A_1}}$
% and are marked by the stars in the Figure \ref{fig:A1+A1-A3_branching}.
% \begin{figure}[b]
% %\begin{figure}[p]
% %  \hspace*{-1cm}
%   \includegraphics[width=135mm,height=85mm]{A1+A1-A3_branching.eps}
%   \caption{Anomalous branching coefficients for $L^{w_2}_{\hat A_3\downarrow \hat{A_1}\oplus\hat{A_1}}$}
%   \label{fig:A1+A1-A3_branching}
% \end{figure}
% 
% Treating analogously the modules $L^{w_0}_{\hat A_3}, L^{w_1}_{\hat A_3}, L^{w_3}_{\hat A_3}$
% we get the following set of branching rules
%  \begin{equation}
%    \label{eq:39}
%    \begin{array}{ll}
%      L^{(0,0,0;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(0;2;0)}\otimes L_{\hat{A_1}}^{(0;2;0)} \\
%      L^{(1,0,0;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(1;2;0)}\otimes L_{\hat{A_1}}^{(1;2;0)} \\
%      L^{(0,1,0;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & \left( L_{\hat{A_1}}^{(2;2;0)}\otimes L_{\hat{A_1}}^{(0;2;0)}\right) \oplus \left( L_{\hat{A_1}}^{(0;2;0)}\otimes L_{\hat{A_1}}^{(2;2;0)}\right) \\
%      L^{(0,0,1;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(1;2;0)}\otimes L_{\hat{A_1}}^{(1;2;0)} \\     
%    \end{array}
%  \end{equation}
% 
% Now we can construct the modular invariant partition function for WZW-model with the chiral algebra $\hat{A}_1\oplus \hat{A}_1$.
% \begin{eqnarray*}
%   \label{eq:40}
%   Z=\left|\chi_{(0;2;0)}\chi_{(0;2;0)}\right|^2+2\left|\chi_{(1;2;0)}\chi_{(1;2;0)}\right|^2+ \left|\chi_{(2;2;0)}\chi_{(0;2;0)}+\chi_{(0;2;0)}\chi_{(2;2;0)}\right|^2=\\
%   \left|\chi_{(0;2;0)}\right|^4+2\left|\chi_{(1;2;0)}\right|^4+ 4\left|\chi_{(2;2;0)}\chi_{(0;2;0)}\right|^2
% \end{eqnarray*}
% 
% By this example we have illustrated the mechanism of our algorithm.
% We want to remind that the proposed method is universal and can be applied to
% an arbitrary pair of affine Lie algebras $\mathfrak{a}\subset\mathfrak{g}$.
% 
\subsection{Coset models}
\label{sec:coset-models}
